Non-target Screening (NonTargetAnalysisResults) Wastewater Treatment Evaluation

### 2025-04-24 dev/demo_nts.Rmd
Update NTS to NonTargetAnalysisResults
other fixes

---
title: 'Non-target Screening (NTS) Wastewater Treatment Evaluation'
author:
  name: Ricardo Cunha
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    fig_caption: true
    toc: true
    number_sections: true
    toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{'Non-target Screening (NTS) Wastewater Treatment Evaluation'}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

The created features and feature groups can be inspected as `data.table` objects or plotted by dedicated methods in the *MassSpecEngine*. Internally, the *MassSpecEngine* stores the results in the *NTS* object, which can be accessed with `MassSpecEngine$NTS`. Yet, the engine interface is recommended for accessing the results. However, the *NTS* object can be used for more advanced operations, such as exporting the results to a database or other formats or use the native objects from other packages (e.g., [patRoon](https://github.com/rickhelmus/patRoon)) as we demonstrate further in this article.

@@

The NTS object holds methods to obtain original objects from the [patRoon](https://github.com/rickhelmus/patRoon) package. For instance, the S4 class `features` or `featureGroups` objects can be obtained via the `get_patRoon_features` method of the *NTS* results. The `patRoon` package provides a comprehensive set of functions, as shown below. See more information in the [patRoon reference documentation](https://rickhelmus.github.io/patRoon/reference/index.html).

```{r pat-features}
# Native patRoon object
fGroups <- get_patRoon_features(ms$NTS, filtered = FALSE, featureGroups = TRUE)

>>>>

---
title: 'Non-target Screening (NonTargetAnalysisResults) Wastewater Treatment Evaluation'
author:
  name: Ricardo Cunha
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    fig_caption: true
    toc: true
    number_sections: true
    toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{'Non-target Screening (NonTargetAnalysisResults) Wastewater Treatment Evaluation'}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

The created features and feature groups can be inspected as `data.table` objects or plotted by dedicated methods in the *MassSpecEngine*. Internally, the *MassSpecEngine* stores the results in the *NonTargetAnalysisResults* object, which can be accessed with `MassSpecEngine$NonTargetAnalysisResults`. Yet, the engine interface is recommended for accessing the results. However, the *NonTargetAnalysisResults* object can be used for more advanced operations, such as exporting the results to a database or other formats or use the native objects from other packages (e.g., [patRoon](https://github.com/rickhelmus/patRoon)) as we demonstrate further in this article.

@@

The NonTargetAnalysisResults object holds methods to obtain original objects from the [patRoon](https://github.com/rickhelmus/patRoon) package. For instance, the S4 class `features` or `featureGroups` objects can be obtained via the `get_patRoon_features` method of the *NonTargetAnalysisResults* results. The `patRoon` package provides a comprehensive set of functions, as shown below. See more information in the [patRoon reference documentation](https://rickhelmus.github.io/patRoon/reference/index.html).

```{r pat-features}
# Native patRoon object
fGroups <- get_patRoon_features(ms$NonTargetAnalysisResults, filtered = FALSE, featureGroups = TRUE)
